jl
```
```{r message=FALSE, warning=FALSE}
library(Lahman)
library(sqldf)
```


```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='NYA' and HR<=40"
sqldf(query)
```

```{r}
query<-"SELECT playerID,yearID,teamID,HR,SO FROM Batting
WHERE HR>40 and SO<60"
sqldf(query)
```

```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting
WHERE teamID='PHI' and yearID>=1970 and yearID<1980 and HR>30"
sqldf(query)
```

## ORDER BY 

With SQL, you can other the rows of your output. For instangce. suppose you want to see every instangce of a like the player hitting more than 50 homeruns. But you would be like the players with most homeruns to be at the top. We could do the following:
```{r}
query<-"SELECT playerID,yearID,teamID,HR FROM Batting 
WHERE HR>50
ORDER BY HR DESC"
sqldf(query)
```

In the exmaple below, we are running a query searching for players that have struck out less than 10 times, have had as least 400 at-bats and we are ordering the list with the least strikouts at the top. For that, we would write the following:
```{r}
query<-"SELECT playerID,yearID,teamID,AB,SO FROM Batting
WHERE SO<10 and AB>400

ORDER BY SO"
sqldf(query)
```

## Aggregation

Sometimes when we working with SQL, there it will be a need to condense results to the minimum possible output. Below you will find some examples of how we can do perform this, with my examples using sum(HR) and avg(HR).
```{r}
query<-"SELECT playerID,sum(HR) FROM Batting GROUP BY playerID
HAVING sum(HR)>=600
ORDER BY sum(HR) DESC"
sqldf(query)
```

```{r}
query<-"SELECT playerID,avg(HR) FROM Batting
GROUP BY playerID
HAVING avg(HR)>30
ORDER BY avg(HR) DESC"
sqldf(query)
```

##Joins

Sometimes when we working with SQL, there are instances where you want to to join multiple tables to come together as one output. Below i will post some examples of code used to go about it.
```{r}
query<-"SELECT nameFirst,nameLast,teamID,yearID,HR
FROM Batting INNER JOIN Master
ON Batting.playerID=Master.playerID
WHERE Batting.playerID='ruthba01'"
sqldf(query)
```

The example about that, we ran a query looking for seasons where Baba Ruth played baseball, joining the Master and Batting tables to come to or resilt.
Im\n the example right down, we have linked the Batting and Master tables again to find instances of players hittinh more than 50 homeruns, including first/last name,team,year,and homerun total.
```{r}
query<-"SELECT nameFirst,nameLast,teamID,yearID,HR
FROM Batting INNER JOIN Master
ON Batting.playerID=Master.playerID
WHERE HR>50
ORDER BY HR DESC"
sqldf(query)

```

For the final of the first set of join queries, we searched for results concerning Baba Ruth, his team name, year played, and homerun totlas.
```{r}
query<-"SELECT playerID,name,Batting.HR
FROM Batting INNER JOIN Teams
ON Batting.teamID=Teams.teamID and Batting.yearID=Teams.yearID
WHERE playerID='ruthba01'"
sqldf(query)
```

##Joins UPDATE September 13, 2017
As stated in the previous update of the website, i have now an inst5ance of code where you would be able to link three tables together. The example is below here:
```{r}
query<-"SELECT nameFirst,nameLast,name,Batting.yearID,Batting.HR
FROM Batting INNER JOIN Teams
ON Batting.teamID=Teams.teamID and Batting.yearID=Teams.yearID
INNER JOIN Master
ON Batting.playerID=Master.playerID
WHERE Batting.playerID='ruthba01'"
sqldf(query)
```

As you can see above, there are two INNER JOIN commands in the syntax of our code, one of which links the Teams table and the other linking the Master table, making connections with teamID, yearID, and playerID.
```{r}
query<-"SELECT nameFirst,nameLast,sum(HR)
FROM Batting INNER JOIN Master
ON Batting.playerID=Master.playerID
GROUP BY Batting.playerID
HAVING sum(HR)>=600
ORDER BY sum(HR) DESC"
sqldf(query)


```

```{r}
query<-"SELECT nameFirst,nameLast,avg(salary)
FROM Salaries INNER JOIN Master
ON Salaries.playerID=Master.playerID
WHERE nameFirst='Bob'
GROUP BY Salaries.playerID
HAVING avg(salary)>1000000
ORDER BY avg(salary) DESC"
sqldf(query)
```

